### 2015-06-26 reports/paper/experiment.tex
udpate
thesis update

In figure~\ref{fig:show_case}, a few examples of drawing letters with music are presented. Green dots on the plots represent the raw localization output and the red line shows the movement output with averaging filtering (window size of $0.5$ seconds is used). The demonstrated letters are drawn with free hand, without a track guiding the movement. The accuracy is reasonably good, and each letter can be easily recognized. There is a bit of jiggling in the tracked movement. Part of the jiggling can be attributed to the noise from system output, and the rest comes from the hand movement.

@@

The color of the painted dots can be controlled by the volume of the sound. Fig~\ref{fig:show_color} presented painting three strips with different colors by varying the volume of the white noise. The color is generated in the Hue Saturation Value color space where the Saturation and Value are set to $0.9$ while the volume controls the hue. Figure~\ref{fig:show_color_1_1} shows the painted first strip where the volume is set to maximum. The color is in the red range. In fig~\ref{fig:show_color_1_2}, we painted another strip after the volume is decreased by $20$ percent. After the volume is decreased, the painted color is in the blue range. In fig~\ref{fig:show_color_1_3}, we painted a third strip after the volume is decreased by another $20$ percent. In the final strip, the color is in the green range. A video demonstration is available at~\cite{demo:color}.

@@

If a music is used, then the volume naturally changes with the content in the music. In figure~\ref{fig:show_color_2}, we painted a heart shape by free hand with a pop song. The song used here is xx by xxx. As can be seen from the figure, the color of the heart changes at each time instant according to the volume of the song. A video demonstration is available at~\cite{demo:color2}.

>>>>

In figure~\ref{fig:show_case}, a few examples of drawing letters with music are presented. Each letter took around $5$ to $10$ seconds to draw, depending on the size of the letter and the speed of the movement. Green dots on the plots represent the raw localization output and the red line shows the movement output with averaging filtering (window size of $0.5$ seconds is used). The demonstrated letters are drawn with free hand, without a track guiding the movement. The accuracy is reasonably good, and each letter can be easily recognized. There is a bit of jiggling in the tracked movement. Part of the jiggling can be attributed to the noise from system output, and the rest comes from the hand movement.

@@

The volume of the acoustic source can also be used to control the color of the dots painted in the above experiment. To show how the volume acts as a color control, a simple experiment is shown in Figure~\ref{fig:show_color}. In this experiment, three stripes are drawn with the same acoustic source but different volume. The color is generated in the Hue-Saturation-Value color space where the Saturation and Value are set to $0.9$ while the hue is controlled by the volume. Figure~\ref{fig:show_color_1_1} shows the first stripe where the volume is set to the maximum and the painted color is in the red range. In fig~\ref{fig:show_color_1_2}, we painted another strip after the volume is decreased by $20$ percent. The painted color changed to the blue range after the volume is decreased. In fig~\ref{fig:show_color_1_3}, we painted a third strip where we further decreased the volume by another $20$ percent. In this final stripe, the color changed to the green range. A video demonstration is available at~\cite{demo:color}.

@@

Instead of manually varying the volume of the acoustic source, a natural extension is to use music as our acoustic source. Generally, the volume of music will vary with time and this change will be reflected by the colors drawn. In figure~\ref{fig:show_color_2}, we used a pop song as our acoustic source and painted a heart shape by free hand. The song used here is \emph{Don't Let It Break Your Heart} by \emph{Coldplay}. As can be seen from the figure, the color of the heart changes at each time instant according to the volume of the song. A video demonstration is available at~\cite{demo:color2}.

### 2015-06-26 reports/paper/introduction.tex
thesis update

In this paper, we first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.

>>>>

\section{Contribution}
In this thesis, we provided a detailed simulation analyzing the impact of the arriving time estimation accuracy on localization error. We evaluated different array architectures, and showed that a two array architecture achieves good localization accuracy while maintaining good portability. We implemented and built the proposed sound localization system and compared different state of the art methods for localization and tracking. We also demonstrated that our system can be used as a tool for painting in space.
In this thesis, we first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.
